---
title: "Coursera Machine Learning"
author: "Liu Yanxiong"
date: "Tuesday, June 16, 2015"
output: html_document
---

##**Read Data**
  
  We first setup the working directory and loading the data
```{r}
setwd("C:/Users/USER/Desktop/Assignment/MachineLearning")
train<-read.csv("pml-training.csv")
test<-read.csv("pml-testing.csv")
```
##**Load the "caret" and partition the data**
  
  We then using the **caret** package to partition the data for training and cross validation
```{r} 
library(caret)
set.seed(123456)
trainset <- createDataPartition(train$classe, p = 0.8, list = FALSE)
Training <- train[trainset, ]
Validation <- train[-trainset, ]
```
##**Preliminary data cleaning
  
  We clean up the the columns with mission values, near zero variance and descriptive data for better machine training experience 
```{r}
nzvcol <- nearZeroVar(Training)
Training <- Training[, -nzvcol]
cntlength <- sapply(Training, function(x) {sum(!(is.na(x) | x == ""))})
nullcol <- names(cntlength[cntlength < 0.6 * length(Training$classe)])
descriptcol <- c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", 
                  "cvtd_timestamp", "new_window", "num_window")
excludecols <- c(descriptcol, nullcol)
```

##**Data Training**
  
  We then carrying out data training using random forest
```{r}
Training <- Training[, !names(Training) %in% excludecols]
library(randomForest)
rfModel <- randomForest(classe ~ ., data = Training, importance = TRUE, ntrees = 10)
```
##**Validation**
  
  Model validation within the training set
```{r}
library("e1071")
ptraining <- predict(rfModel, Training)
print(confusionMatrix(ptraining, Training$classe))
```
  
  Model validtion out of the trainig set
```{r}
pvalidation <- predict(rfModel, Validation)
print(confusionMatrix(pvalidation, Validation$classe))
```
  
  As we can see from the above two tables, the model works well for the validation

##**Set prediction**
  
  The following provides with the result on prediction
```{r}
ptest <- predict(rfModel, test)
ptest
```